\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-16 paper/paper.tex
tweak

We did notice that Minstrel occasionally has very poor performance on
traces 1 seconds or shorter---sometimes as low as 2 Mbps. This is
because it does not stop sending after four successive failures, but
must wait until the end of the 100ms window for statistics to be
compiled. Thus it wastes a lot of time sending at non-optimal rates;
and a short trace has only a few 100ms windows. This behavior is not
evident in long traces, however, as Minstrel has had time to both
smooth out bad windows and collect more statistics (making it less
likely to choose a bad rate).

@@

We implemented SampleRate as outlined in the thesis, but the MadWifi
implementation has a few key differences from the thesis. We suspect
that the MadWifi use of an EWMA instead of a window has more accurate
rate statistics, which will potentially lead to better throughput. We
did not have the time to implement this alternative version, but it is
worth further examination.

>>>>

@@

We implemented SampleRate as outlined in the thesis, but the MadWifi
implementation has a few key differences from the thesis. MadWifi 
use of an EWMA instead of a window has more accurate
rate statistics, which will potentially lead to better throughput. We
did not have the time to implement this alternative version, but it is
worth further examination.
